On the performance of the MAC model

### 2018-10-29 2018_nips_vigil/mac.tex

>>>>

\textbf{\textit{Description of the input unit:}}

The role of the input unit is to preprocess the raw images and questions. 
The images are passed through a feature extractor (ResNet101 cut after layer \textbf{\textit{con4}} ) pre-trained on ImageNet. The output tensor is a feature map that is finally processed by two trainable CNN layers to obtain the knowledge base \textbf{\textit{K}}, the final image representation.

The question first go through a word embedding method and then a bidirectional LSTM.
The question preprocessing leads to two different outputs:

\begin{description}
	\item[$\bullet$] The question representation \textbf{\textit{q}} which is the concatenation of the final hidden states from the backward and forward LSTM passes
	\item[$\bullet$] The contextual words \textbf{\textit{cw}} : a series of output states \textbf{\textit{cw1}}, . . . , \textbf{\textit{cwS}} that represent each word in the context of the question
\end{description}

\textbf{\textit{Description of the output unit:}}

The output unit simply process the concatenation of the question representation  \textbf{\textit{q}} and the final memory  \textbf{\textit{mp}} to produce a final answer. For CLEVR it is a 2-layer fully-connected softmax classifier.
